Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-15 Paper/RSVOptimization.rnw
Heading tweaks

\paragraph{Spatially adjusted regimens are superior to the AAP recommendations}

@@

\paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}

>>>>

\paragraph{Without calendarical rounding, spatially adjusted regimens are superior to the AAP recommendations}

@@

\paragraph{Calendrical rounding rapidly diminishes gains over the AAP-recommended regimen}
